Program Equivalence : Relational Separation Logic interactive prover implemented in Maude

### 2018-06-10 paper/paper.tex
finished Relational Separation Logic paper part

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage{array}
\usepackage{tabularx}
\usepackage{ebproof}
\author{ANDREI-ALIN CORODESCU}
\title{Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}
\begin{document}
\begin{titlepage}
\begin{center}
\textbf{
"ALEXANDRU IOAN CUZA" UNIVERSITY OF IAȘI
}
\\
\textbf{FACULTY OF COMPUTER SCIENCE}
\end{center}
   \vspace{40mm}
\begin{center}
	\Large\textbf {Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}\\
	\vspace{40mm}
	\large\textit {ANDREI-ALIN CORODESCU}
	\\
	\vspace{20mm}
	\textbf{Session: }\textit{July, 2018}\\
	\vspace{30mm}
	\textbf{Scientific Coordinator}\\
	\textbf{\textit{Conf. Dr. Ciobâcă Ștefan}}
	\vspace{30mm}
\end{center}
\end{titlepage}
\tableofcontents
\pagebreak

@@

\(R\) represents a \textbf{relation} between the two program states holding before the execution of \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands. 
\subsection{Rewriting Logic}
\section{Relational Separation Logic Interactive Prover}
Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
\subsection{Maude - General Overview}
\subsection{Executable semantics of the language}
\subsection{Modelling the Separation Logics}
\subsection{Interaction by Maude LOOP-MAUDE}
\subsection{Prover execution flow}
\subsection{Automated processes}
\subsubsection{Automatic matching of axioms and previously proven goals}
\subsubsection{Automatic demonstration of implications}
\subsection{User Interface}
\subsection{Future directions}
\section{Additional Research}
\subsection{Automatic prover}
\subsection{Concurrent programs extension}
\subsection{Java+ITP}

>>>>

\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[english]{babel}
\usepackage{array}
\usepackage{tabularx}
\usepackage{ebproof}
\author{ANDREI-ALIN CORODESCU}
\title{Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}
\newcommand{\hq}[4]{
	\left\{{#1}\right\}
	\let\scriptstyle\textstyle 
	\substack{{#2} \\ 	\let\scriptstyle\textstyle {#3}} 
	\left\{{#4}\right\}
}

\begin{document}
\begin{titlepage}
\begin{center}
\textbf{
"ALEXANDRU IOAN CUZA" UNIVERSITY OF IAȘI
}
\\
\textbf{FACULTY OF COMPUTER SCIENCE}
\end{center}
   \vspace{40mm}
\begin{center}
	\Large\textbf {Program Equivalence : Relational Separation Logic interactive prover implemented in Maude}\\
	\vspace{40mm}
	\large\textit {ANDREI-ALIN CORODESCU}
	\\
	\vspace{20mm}
	\textbf{Session: }\textit{July, 2018}\\
	\vspace{30mm}
	\textbf{Scientific Coordinator}\\
	\textbf{\textit{Conf. Dr. Ciobâcă Ștefan}}
	\vspace{30mm}
\end{center}
\end{titlepage}
\tableofcontents
\pagebreak

@@

\(R\) represents a \textbf{relation} between the two program states holding before the execution of \(C_1\) and \(C_2\) respectively while \(T\) represents a \textbf{relation} which holds after the execution of the two commands. 
\\

Since relational separation language reasons about two programs simultaneously, it employs a storage model in which both programs share a single \(Store\) but have independent \(Heaps\). This implies that the programs need to use \textbf{disjoint} parts of the same \(Store\). The benefit of such a model is that we can use variables in Relations which aren't used by the two programs directly to relate them.
\begin{figure}[h]
	\noindent\rule{\linewidth}{0.4pt}
	\medskip
	\begin{tabularx}{\linewidth}{l  X}
		Relation& \(R ::= Same \mid Emp \mid \left( P_1 \atop P_2 \right) \mid R_1 * R_2 \mid B \mid R_1 \Rightarrow R_2 \mid R_1 \land R_2 \mid R_1 \lor R_2 \mid \neg R \mid \exists x. R \mid \forall x. R \) \\
	\end{tabularx}
	\caption{Syntax of the relation language}
	\label{fig:RelationSyntax}
	\noindent\rule{\linewidth}{0.4pt}
\end{figure}
\paragraph{Semantics of the Relation Language}
The semantics of the Relation Language are derived from the semantics of the Assertion Language, and in the following section I will present the newly introduced elements. 
\begin{itemize}
	\item{ \(Same\) denotes that the heaps associated with the 2 programs are identical}
	\item{ \(Emp\) is the Relational equivalent of the \(emp\) assertion; specifies two empty heaps}
	\item{ \(\left(P_1 \atop P_2\right)\) is the building block of the Relational separation logic: it allows to construct a relation between programs by putting together 2 assertions, \(P_1\) holding for the first program and \(P_2\) holding for the second program}
	\item{ \(R_1 * R_2\) represents the relational separating conjunction and it keeps a similar meaning to the Separation Logic one ; it separates two relations referring to \textbf{disjoint} parts of the heaps of the two programs.}
\end{itemize}
\begin{figure}
		\noindent\rule{\linewidth}{0.4pt}
	Loop:
	\[
	\begin{prooftree}
	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
	\Hypo{\{R \land B \} {C \atop C\prime} {R}}
	\Infer 2 {\{R\}
		\let\scriptstyle\textstyle 
		\substack{\mathtt{while\ B\ do\ C\ od} \\ \mathtt{while\ B\prime\ do\ C\prime\ od}} \{R \land \neg B\}}
	\end{prooftree}	
	\]
	Conditional Statement
	\[
	\begin{prooftree}
	\Hypo{R \Rightarrow (B \Leftrightarrow B\prime)}
	\Hypo{ \{R \land B\} 		
		\let\scriptstyle\textstyle 
		\substack{C_1 \\ C_1\prime} \{S\}
		}
	\Hypo{
		\{R \land \neg B\}
		\let\scriptstyle\textstyle 
		\substack{C_2 \\ C_2\prime}
		\{S\}
	}
	\Infer 3 {\{R\}\  	
				\let\scriptstyle\textstyle 
				\substack{\mathtt{if\ B\ then\ C_1\ else\ C_2\ fi} \\ \mathtt{if\ B\prime\ then\ C_1\prime\ else\ C_2\prime fi}} \{S\}}
	\end{prooftree}	
	\]
	Sequencing Rule
	\[
	\begin{prooftree}
	\Hypo{ \hq{R}{C_1}{C_1\prime}{S}}
	\Hypo{ \hq{S}{C_2}{C_2\prime}{T}}
	\Infer 2 {\hq{R}{C_1 ; C_2}{C_1\prime ; C_2\prime}{T}}
	\end{prooftree}	
	\]
	Frame Rule
	\[
	\begin{prooftree}
	\Hypo { \hq{R}{C}{C\prime}{S}}
	\Infer 1 {\hq{R * T} {C}{C\prime}{S * T}}
	\end{prooftree}	
	\]
	Embedding rule
	\[
	\begin{prooftree}
	\Hypo{\{P\} C \{Q\}}
	\Hypo{\{P\prime\} C\prime \{Q\prime\}}
	\Infer 2 {\hq{\left( \substack{P \\ P\prime}\right)}{C}{C\prime}{\left( \substack{Q \\ Q\prime}\right)}}
	\end{prooftree}	
	\]
	Consequence Rule
	\[
	\begin{prooftree}
	\Hypo{R \Rightarrow R_1}
	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
	\Hypo{S \Rightarrow S_1}
	\Infer 3 {\hq{R}{C}{C\prime}{S}}
	\end{prooftree}	
	\]
	Conjunction Rule
	\[
	\begin{prooftree}
	\Hypo{\hq{R_1}{C}{C\prime}{S_1}}
		\Hypo{\hq{R_2}{C}{C\prime}{S_2}}
	\Infer 2 {\hq{R_1 \land R_2}{C}{C\prime}{S_1 \land S_2}}
	\end{prooftree}	
	\]
	Auxiliary Variable Elimination
	\[
	\begin{prooftree}
	\Hypo{\hq{R}{C}{C\prime}{S}}
	\Infer 1 {\hq{\exists x.R}{C}{C\prime}{\exists x.S}}
	\end{prooftree}	
	\]
	\caption{Relational Separation Logic Proof Rules}
	\label{fig:ProofRue}
	\noindent\rule{\linewidth}{0.4pt}
\end{figure}

Most of the rules are adapted from the Separation Logic ones, and the link between the two logics is given by the \textbf{Embedding Rule}, which allows to transform a Relational Separation Logic Hoare Quadruple into two Separation Logic Hoare Triples. The rules are presented in Figure \ref{fig:ProofRue}. 
\clearpage
\subsection{Rewriting Logic}

\section{Relational Separation Logic Interactive Prover}
Ordinea subsectiunilor mai poate fi schimbata ulterior. Capitolul cel mai semnificativ din lucrare, va contine toate detaliile de implementare ale solutiei curente
\subsection{Maude - General Overview}
\subsection{Executable semantics of the language}
\subsection{Modelling the Separation Logics}
\subsection{Interaction by Maude LOOP-MAUDE}
\subsection{Prover execution flow}
\subsection{Automated processes}
\subsubsection{Automatic matching of axioms and previously proven goals}
\subsubsection{Automatic demonstration of implications}
\subsection{User Interface}
\subsection{Future directions}
\section{Additional Research}
\subsection{Automatic prover}
\subsection{Concurrent programs extension}
\subsection{Java+ITP}
